---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# getRad

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/getRad)](https://CRAN.R-project.org/package=getRad)
[![R-CMD-check](https://github.com/aloftdata/getRad/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/aloftdata/getRad/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/aloftdata/getRad/branch/main/graph/badge.svg)](https://app.codecov.io/gh/aloftdata/getRad/)
[![repo status](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

getRad is an R package that provides a unified interface to download radar data for biological and aeroecological research. It gives access to both polar volume radar data and [vertical profile data](https://aloftdata.eu/vpts-csv/) from [different repositories](https://aloftdata.github.io/getRad/articles/supported_countries.html) and loads it directly into R. getRad also facilitates further exploration of the data by other tools such as [bioRad](https://adokter.github.io/bioRad) by standardizing the data.

## Installation

You can install the released version of getRad from CRAN with:

``` r
install.packages("getRad")
```

Alternatively, you can install the development version of getRad from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("aloftdata/getRad")
```

Then load the package:

``` r
library(getRad)
```

## Usage

Download a polar volume, and then plot it using `bioRad`:

```{r example}
library(getRad)
library(bioRad)
# Plot insect movements in Finland (Mäkinen et al. 2022)
pvol <- get_pvol("fianj", as.POSIXct("2012-5-17 14:15", tz = "UTC"))
plot(project_as_ppi(get_scan(pvol, 0), range_max = 75000))
plot(calculate_vp(pvol, h_layer = 50, n_layer = 40))
```

Download a vertical profile time series from the [Aloft](https://aloftdata.eu/) bucket:

```{r vpts}
vpts_list <- get_vpts(c("bewid", "deess"),
  lubridate::interval(lubridate::as_datetime("2016-10-03 16:00:00"), 
                      lubridate::as_datetime("2016-10-05 10:00:00")),
  source = "ecog-04003"
)
par(mfrow = 2:1)
for(i in names(vpts_list))
  plot(regularize_vpts(vpts_list[[i]]), main=i)
```

## Meta

- We welcome [contributions](https://aloftdata.github.io/getRad/CONTRIBUTING.html) including bug reports.
- License: MIT
- Get [citation information](https://aloftdata.github.io/getRad/authors.html#citation) for getRad in R doing `citation("getRad")`.
- Please note that this project is released with a [Contributor Code of Conduct](https://aloftdata.github.io/getRad/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
