---
title: "VPTS file coverage"
---

```{r pkgsetup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, echo = F,
  comment = "#>"
)
```

Various sources of VPTS files cover different radars and time periods. Here we visualize the temporal coverage per source and radar. If you click on a radar on the map a plot shows the percentage of days with available data per month. Note that this article gets generated irregularly and is up to date until `r  Sys.Date()`.

For a more detailed description of the data in Aloft bucket and its pitfalls see the [FAQ](https://aloftdata.eu/faq/).

```{r setup, message=FALSE}
library(getRad)
require(leafpop)
require(leaflet)
require(ggplot2)
require(dplyr)
library(htmltools)
```

```{r data}
cvr <- get_vpts_coverage("all")
wr <- get_weather_radars("all") |>
  group_by(radar) |>
  arrange(status) |>
  slice_tail(n = 1)
```
```{r}
# there is a with issue in the svg, here is a temporary solution: https://github.com/r-spatial/leafpop/issues/25
assignInNamespace("popupSVGraph",function(graphs, #dsn = tempdir(),
                        width = 300, height = 300, ...) {
  lapply(1:length(graphs), function(i) {
    #nm = paste0("tmp_", i, ".svg")
    #fls = file.path(dsn, nm)

    inch_wdth = width / 96
    inch_hght = height  / 96

    #svg(filename = fls, width = inch_wdth, height = inch_hght, ...)
    #print(graphs[[i]])
    #dev.off()
    lns <- svglite::svgstring(
      width = inch_wdth,
      height = inch_hght,
      standalone = FALSE
    )
    print(graphs[[i]])
    dev.off()

    svg_str <- lns()

    # this is a temporary solution to work around svglite
    #   non-specific CSS styles
    #   perhaps we should separate out into its own function/utility
    #   also adds uuid dependency
    svg_id <- paste0("x",uuid::UUIDgenerate())
    svg_str <- gsub(
      x = svg_str,
      pattern = "<svg ",
      replacement = sprintf("<svg id='%s'", svg_id)
    )
    # this style gets appended as defaults in all svglite
    #    but might change if svglite changes
    svg_css_rule <- sprintf(
      "#%1$s line, #%1$s polyline, #%1$s polygon, #%1$s path, #%1$s rect, #%1$s circle {",
      svg_id
    )
    svg_str <- gsub(
      x = svg_str,
      pattern = "line, polyline, polygon, path, rect, circle \\{",
      replacement = svg_css_rule
    )

    #lns = paste(readLines(fls), collapse = "")
    # file.remove(fls)
    #     return(
    # sprintf(
    # "
    # <div style='width: %dpx; height: %dpx;'>
    # %s
    # </div>
    # " ,
    #   width,
    #   height,
    #   svg_str
    # )
    # )
    pop = sprintf(
      "<div style='width: %dpx; height: %dpx;'>%s</div>",
      width,
      height,
      svg_str
    )

    popTemplate = system.file("templates/popup-graph.brew", package = "leafpop")
    myCon = textConnection("outputObj", open = "w")
    brew::brew(popTemplate, output = myCon)
    outputObj = outputObj
    close(myCon)

    return(paste(outputObj, collapse = ' '))

  })
}
,"leafpop")
```


```{r}
cvr_summary <- cvr |>
  group_by(radar, source,
    month = factor(month.name[lubridate::month(date)],
      levels = month.name
    ), year = lubridate::year(date)
  ) |>
  summarise(n = n(), n_max = unique(lubridate::days_in_month(date)), .groups = "drop")
```

```{r create_maps}
html <- list()
for (i in unique(cvr$source)) {
  cvrsub <- cvr_summary |> dplyr::filter(source == i)
  years <- seq(min(cvrsub$year), max(cvrsub$year), 1)
  cvrsub |>
    group_by(radar) |>
    summarize(grph = list(ggplot(data = bind_rows(expand.grid(year=years, month=month.name, n=NA, n_max=NA), pick(everything())))+
      scale_x_discrete("Month", breaks = month.name, labels = month.name, limits = month.name) +
      geom_raster(aes(x = month, y = year, fill = (n / n_max) * 100)) +
      scale_fill_viridis_c("Coverage", limits = c(0, 100), breaks = (0:5) * 20, labels = paste0((0:5) * 20, " [%]"), direction = -1, na.value = "#FFF0") +
      theme_minimal() +
      scale_y_continuous("Year", breaks=if(length(years)<6){ years}else{pretty(years)} , limits = range(years) + c(-.51, .51)) +
      theme(
        axis.text.x = element_text(angle = -90, vjust = 0.5, hjust = 0),
        plot.title = element_text(hjust = 0.5),
        panel.grid = element_blank(), 
        legend.ticks = element_blank()
      ) +
      ggtitle(radar) )) -> res
#  res$grph[[1]]
  suppressWarnings(res |> left_join(wr |> select(radar, longitude, latitude), by = join_by(radar))) -> res
  ll <- NULL
  if (any(is.na(res$longitude))) {
    ll <- p(glue::glue("The following radars were omitted from the map because they lack location information in OPERA: {glue::glue_collapse(res$radar[is.na(res$longitude)], ', ', last = ' and ' )}."))
  }
  res <- res |> filter(!is.na(longitude))
  lft <- leaflet() |>
    addTiles() |>
    addCircleMarkers(
      lng = res$longitude,
      lat = res$latitude,
      label = res$radar,
      clusterOptions = markerClusterOptions(maxClusterRadius = 30),
      popup = popupGraph(res$grph, type = "svg")
    )
  html <- c(html, list(h3(i), lft, ll))
}
tagList(html)
```
