---
title: "VPTS file coverage"
---

```{r pkgsetup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, echo = F,
  comment = "#>"
)
```

Various sources of VPTS files cover different radars and time periods. Here we visualize the temporal coverage per radar and data source. If you click on a radar on the map a plot shows the percentage of days with available data per month. Note that this article gets generated irregularly and is up to date until `r  Sys.Date()`.

For a more detailed description of the data in Aloft bucket and its pitfalls see the [FAQ](https://aloftdata.eu/faq/).

```{r setup, message=FALSE}
library(getRad)
require(leafpop)
require(leaflet)
require(ggplot2)
require(dplyr)
library(htmltools)
```

```{r data}
cvr <- get_vpts_coverage(source = "all")
wr <- get_weather_radars("opera") |>
  group_by(radar) |>
  arrange(status) |>
  slice_tail(n = 1)
```


```{r}
cvr_summary <- cvr |>
  group_by(radar, source,
    month = factor(month.name[lubridate::month(date)],
      levels = month.name
    ), year = lubridate::year(date)
  ) |>
  summarise(n = n(), n_max = unique(lubridate::days_in_month(date)), .groups = "drop")
```

```{r create_maps}
html <- list()
for (i in unique(cvr$source)) {
  cvrsub <- cvr_summary |> dplyr::filter(source == i)
  years <- seq(min(cvrsub$year), max(cvrsub$year), 1)
  cvrsub |>
    group_by(radar) |>
    summarize(grph = list(ggplot(data = pick(everything())) +
      geom_tile(aes(x = month, y = year, fill = (n / n_max) * 100)) +
      scale_fill_viridis_c("Coverage", limits = c(0, 100), breaks = (0:5) * 20, labels = paste0((0:5) * 20, " [%]"), direction = -1) +
      theme_minimal() +
      scale_y_continuous("Year", breaks = years, limits = range(years) + c(-.51, .51)) +
      theme(
        axis.text.x = element_text(angle = -90, vjust = 0.5, hjust = 0),
        plot.title = element_text(hjust = 0.5),
        panel.grid = element_blank()
      ) +
      ggtitle(radar) +
      scale_x_discrete("Month", breaks = month.name, labels = month.name, limits = month.name))) -> res
  res$grph[[1]]
  suppressWarnings(res |> left_join(wr, by = join_by(radar))) -> res
  ll <- NULL
  if (any(is.na(res$longitude))) {
    ll <- p(glue::glue("The following radars were omitted from the map because they lack location information in OPERA: {glue::glue_collapse(res$radar[is.na(res$longitude)], ', ', last = ' and ' )}."))
  }
  res <- res |> filter(!is.na(longitude))
  lft <- leaflet() |>
    addTiles() |>
    addCircleMarkers(
      lng = res$longitude,
      lat = res$latitude,
      label = res$radar,
      clusterOptions = markerClusterOptions(maxClusterRadius = 30),
      popup = popupGraph(res$grph)
    )
  html <- c(html, list(h3(paste0("Source: `", i, "`")), lft, ll))
}
tagList(html)
```
